SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-08-13 scipy-1.0/paper.tex
Update scipy-1.0/paper.tex
Co-Authored-By: Matt Haberland <mdhaber@mit.edu>

Nevertheless, SciPy continually strives to improve.
The SciPy Roadmap\cite{SciPy_roadmap_1,SciPy_roadmap_dev}, summarized in Table~\ref{table:roadmap}, is a
continuously updated document
maintained by the community that describes some of the major directions for
improvement for the project, as well as specific limitations and matters that
require assistance moving forward.
In addition to the items on the roadmap,
we are still working to increase the number of SciPy usage tutorials beyond
our current 15 section offering\cite{SciPy_tutorials}.
Also, the low-level Cython code in our library (which interacts with C-level code and
exposes it for Python usage) could use some measure of modernization, including
migration to typed memoryviews to handle NumPy arrays.

>>>>

Nevertheless, SciPy continually strives to improve.
The SciPy Roadmap\cite{SciPy_roadmap_1,SciPy_roadmap_dev}, summarized in Table~\ref{table:roadmap}, is a
continually updated document
maintained by the community that describes some of the major directions for
improvement for the project, as well as specific limitations and matters that
require assistance moving forward.
In addition to the items on the roadmap,
we are still working to increase the number of SciPy usage tutorials beyond
our current 15 section offering\cite{SciPy_tutorials}.
Also, the low-level Cython code in our library (which interacts with C-level code and
exposes it for Python usage) could use some measure of modernization, including
migration to typed memoryviews to handle NumPy arrays.
